The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-05-10 paper/paper.Rmd
Adding future work rubric

```{r scbi-trees, out.width="66%", fig.cap="Compute growth of trees based on census data. A map of the growth of a random sample of 500 trees from a 9 ha subsection of the Smithsonian Conservation Biology Institute (SCBI) forest plot."}
ggplot() +
  geom_sf(data = growth_scbi %>% sample_n(500), aes(size = growth)) + 
  scale_size_binned(limits = c(0.1, 1)) +
  labs(size = expression(paste(Growth, " (cm ",y^{-1},')')) )
```

@@

```{r scbi-spatial-information, out.width="66%", fig.cap="Add spatial information. A buffer region and spatial cross-validation blocks 1 througth 4. The location of each tree is marked with its fold number where the folds are delineated with solid lines. The color of each digit indicates whether the tree is part of the buffer region (thus will only be considered as a competitor tree) or is part of the interior of the study region (thus is a focal tree whose growth is of modeled interest)."}
ggplot() +
  geom_sf(data = blocks_scbi, fill = "transparent", linetype = "dashed") +
  geom_sf_text(data = growth_scbi %>% sample_n(1000), 
               aes(label = foldID, col = buffer))
```

@@

```{r scbi-focal-vs-comp-map, out.width="66%", echo = FALSE, fig.cap="Identify all focal and corresponding competitor trees. The dashed circle extends 7.5m away from the focal tree 4 while all 20 competitor trees are within this circle."}
comp_radius <- growth_scbi %>% 
  filter(stemID == 4) %>% 
  st_buffer(dist = comp_dist)

@@

```{r scbi-posterior-viz, out.width="100%", fig.cap= "Fit model. Posterior distributions of all parameters. For compactness we include only three species.", fig.width = 8, fig.height = 6}
# Plot posteriors for only a subset of species
sp_to_plot <- c("litu", "quru", "cagl")

@@

This process is repeated for each of the four folds acting as the test set, then the four RMSE's are averaged to provide a single estimate of model error. This algorithm is implemented in `run_cv()`, which acts as a wrapper function to both `comp_bayes_lm()` that fits the model and `predict()` that returns predicted values.

@@

```{r scbi-simulation, out.width="100%", fig.cap="Root mean squared error of models for standard, permuted, and spatial cross-validated error estimates. The dotted lines show non-permuted competitor identity, while the histogras so the RMSE for 49 permutations. The colors indicate whether cross validaton was used.", echo = FALSE}
include_graphics("simulation_results/2021-03-03_scbi_49_shuffles.png")
```

# Conclusion

>>>>

```{r scbi-trees, out.width="66%", fig.cap="Step 1 - Compute growth of trees based on census data. A map of the growth of a random sample of 500 trees from a 9 ha subsection of the Smithsonian Conservation Biology Institute (SCBI) forest plot."}
ggplot() +
  geom_sf(data = growth_scbi %>% sample_n(500), aes(size = growth)) + 
  scale_size_binned(limits = c(0.1, 1)) +
  labs(size = expression(paste(Growth, " (cm ",y^{-1},')')) )
```

@@

```{r scbi-spatial-information, out.width="66%", fig.cap="Step 2 - Add spatial information. A buffer region and spatial cross-validation blocks 1 through 4. The location of each tree is marked with its fold number where the folds are delineated with solid lines. The color of each digit indicates whether the tree is part of the buffer region (thus will only be considered as a competitor tree) or is part of the interior of the study region (thus is a focal tree whose growth is of modeled interest)."}
ggplot() +
  geom_sf(data = blocks_scbi, fill = "transparent", linetype = "dashed") +
  geom_sf_text(data = growth_scbi %>% sample_n(1000), 
               aes(label = foldID, col = buffer))
```

@@

```{r scbi-focal-vs-comp-map, out.width="66%", echo = FALSE, fig.cap="Step 3 - Identify all focal and corresponding competitor trees. The dashed circle extends 7.5m away from the focal tree 4 while all 20 competitor trees are within this circle.", fig.height=4}
comp_radius <- growth_scbi %>% 
  filter(stemID == 4) %>% 
  st_buffer(dist = comp_dist)

@@

```{r scbi-posterior-viz, out.width="100%", fig.cap= "Step 4 - Fit model. Posterior distributions of all parameters. For compactness we include only three species.", fig.width = 8, fig.height = 6}
# Plot posteriors for only a subset of species
sp_to_plot <- c("litu", "quru", "cagl")

@@

This process is repeated for each of the four folds acting as the test set, then the four RMSE's are averaged to provide a single estimate of model error. This algorithm is implemented in `run_cv()`, which acts as a wrapper function to both `comp_bayes_lm()` that fits the model and `predict()` that returns predicted values. Furthermore, `comp_dist` can now be specified as a vector of competitive distances to consider.

@@

```{r scbi-simulation, out.width="100%", fig.cap="Comparison of root mean squared error of models for standard, permuted, and spatially cross-validated error estimates. The dotted lines show observed RMSE while the histograms show the null distribution of RMSE for 49 permutations under the null hypothesis of no competitor species identity effects. The colors indicate whether spatial cross-validation was used or not.", echo = FALSE}
include_graphics("simulation_results/2021-03-03_scbi_49_shuffles.pdf")
```

# Conclusion and future work
